On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-04-04 manuscripts/PNAS/chazthm_pnas.tex
chaz things

\begin{theorem}\label{DeterministicUniquenessTheorem}
%Fix integers $n, \ell$, and $k < m$. 
Let $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfy \eqref{SparkCondition} for $k < m$, and suppose for some $\bar m$ more than \mbox{$(k-1){\bar m \choose k}$} $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} are supported in general linear position on each set in an $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.  There is a constant $C_1 > 0$ for which the following hold for $\varepsilon < L_2(\mathbf{A}) / C_1$.

1.) Every matrix $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ must have $\bar m \geq m$ and, provided $p = \bar m - \ell(\bar m - m)$ is positive, necessarily satisfy:
\begin{align}\label{Cstable}
\|(\mathbf{A}_J- \mathbf{B}_{\bar J} \mathbf{PD} )_j\|_2 \leq C_1 \varepsilon, \ \  \text{for $j \in J$},
\end{align}
for some $J \in {[m] \choose p}$, $\bar J \in {[\bar m] \choose p}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.

2.) Restricting dictionaries and sparse codes to respective $J, \bar{J}$, we furthermore have that if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and:
\begin{align}\label{b-PDa}
\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,\ \ \   \text{for $i \in [N]$}.
\end{align}
\end{theorem}

@@

%\begin{proposition}
%If $E$ is an $\ell$-regular hypergraph of rank $k$ satisfying the singleton intersection property then $|E| \geq \ell m/k$. 
%\end{proposition}
%Note that every $\ell$-regular hypergraph $E \subseteq {[m] \choose k}$ satisfies: \[|E|k = \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m.\] 
As mentioned above, it is easy to construct a regular hypergraph $E \subseteq {[m] \choose k}$ with the SIP having cardinality $|E| = m$, implying the lower bound for sample size $N$ from the introduction. In certain cases, the SIP can be achieved with $|E| < m$; for example, when $k = \sqrt{m}$ one can take $E$ to be the rows and columns formed by arranging $[m]$ in a square grid.  
%In light of Cor.~\ref{DeterministicUniquenessCorollary}, it would be interesting to determine other such $E$. %[ ** TODO ** can we show for every $k, m$ that there is an $E$ satisfying the SIP with $|E| = \ell m/k$ for every $\ell$ such that $\ell m/k$ is an integer? Then lower bound on $N$ comes from the smallest such $\ell$.]

@@

\begin{corollary}\label{SLCopt}
Consider the assumptions as in Thm.\ref{DeterministicUniquenessTheorem} with $1 + (k-1){\bar m \choose k} + |E|k(k-1){\bar m \choose k-1}$ vectors supported on each $S \in E$.
%Suppose $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition} for some $k < m$ and that $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ contain more than $(k-1){m \choose k} + |E|k(k-1){m \choose k-1}$ vectors supported in general linear position on each set in some $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.  Then there exists a constant $C_1 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_1$.
All matrices $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ solving:
\begin{align}\label{minsum}
\min \sum_{i = 1}^N \|\mathbf{\bar x}_i\|_0 \ \ 
\text{subject to} \ \ \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon, \ \text{for all $i$},
\end{align}
%
necessarily satisfy implications 1.) and 2.) from Thm.~\ref{DeterministicUniquenessTheorem}.
%must have $\bar m \geq m$ and, provided $p = \bar m - \ell(\bar m - m) > 0$, necessarily satisfy \eqref{Cstable}
%%\begin{align}\label{Cstable}
%%\|(\mathbf{A}_J- \mathbf{B}_{\bar J} \mathbf{PD} )_j\|_2 \leq C_1 \varepsilon, \ \  \text{for  $j \in J$},
%%\end{align}
%for some $J \in {[m] \choose p}$, $\bar J \in {[\bar m] \choose p}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
\end{corollary}

@@

\begin{corollary}\label{ProbabilisticCor}
Fix $n, m$, and $k$ satisfying \eqref{CScondition} for $\gamma = \gamma_0$, and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$. If more than $(k-1){m \choose k} + 1$ of the vectors $\mathbf{x}_i$ are supported on each $S \in E$ for a regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
\end{corollary}

@@

\section{Proof of Theorem~\ref{DeterministicUniquenessTheorem}}\label{DUT}

@@

The constant $C_1$ in Thm.~\ref{DeterministicUniquenessTheorem} is then given by\footnote{Note that $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for $S \in E$ and $k$-sparse $\mathbf{c}$. Therefore, $\sqrt{k} L_k(\mathbf{AX}_{I(S)}) \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$ since $L_k(\mathbf{A}), L_k(\mathbf{X}_{I(S)}) > 0$ by \eqref{SparkCondition} and general linear position of the $\mathbf{x}_i$.  Thus, $C_1 > 0$.  }:
\begin{align}\label{Cdef1}
C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E) := \frac{ C_2(\mathbf{A}, E) } { \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) },
\end{align}
%
where $\mathbf{X}$ is the $m \times N$ matrix with columns $\mathbf{x}_i$ and $I(S)$ is defined as those $i \in [N]$ with supports in $S$. The constant $C_2 = C_2(\mathbf{A}, E)$ is defined below in terms of one used in \cite{Deutsch12} to analyze the convergence of the alternating projections algorithm.
% for projecting a point onto the intersection of a set of subspaces. 
We use it to bound the distance between a point and the intersection of a set of subspaces given an upper bound on its distance from each subspace individually.

@@

\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
%We begin by showing that for every $S \in E$ there is some $S' \in {[m] \choose k}$ for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_S'\})$ is controlled by $\varepsilon$. Fix $S \in E$. Since there are $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $S' \in {[m] \choose k}$ and some set of $k$ indices $J(S)$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\bar x}_i$ with $i \in J(S)$ are contained in $S$ and $S'$, respectively.
%%% No |S| = k assumption %%%
We shall show that for every $S \in E$ there is some $\bar S \in {[m] \choose k}$, for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\bar S}\})$ is controlled by $\varepsilon$. Applying Lem.~\ref{MainLemma} with the map $\pi$ defined by $S \mapsto \bar S$ then completes the proof.  Since there are $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $\bar S \in {[m] \choose k}$ and some set of $k$ indices $I(S)$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\bar x}_i$ with $i \in I(S)$ are contained in $S$ and $\bar S$, respectively.

Let $\mathbf{X}$ and $\mathbf{\bar{X}}$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\bar x}_i$, respectively. It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{I(S)}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_{S}\}$. Fixing $\mathbf{y} \in \text{\rm Span}\{\mathbf{A}_{S}\}$, there exists $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_{I(S)}\mathbf{c}$. Setting \mbox{$\mathbf{\bar{y}} = \mathbf{B\bar{X}}_{I(S)}\mathbf{c} \in \text{\rm Span}\{\mathbf{B}_{\bar S}\}$}, we have:
\begin{align*}
\|\mathbf{y} - \mathbf{\bar{y}}\|_2 
&= \|\sum_{i=1}^k c_i(\mathbf{AX}_{I(S)} - \mathbf{B\bar{X}}_{I(S)})_i\|_2
\leq \varepsilon \sum_{i=1}^k |c_i| \\
&\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2 
%\leq \frac{\varepsilon \sqrt{k}}{L(\mathbf{A}X_{J(S)})} \|\mathbf{A}X_{J(S)}\mathbf{c}\|_2 
\leq \frac{\varepsilon}{L_k(\mathbf{AX}_{I(S)})} \|\mathbf{y}\|_2,
\end{align*}
where the last inequality is by definition of $L_k$. Finally, from Def.~\ref{dDef}, it follows that for all $S \in E$,
\begin{align}\label{rhs222}
d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\bar S}\}) 
\leq \frac{\varepsilon}{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }.
%\leq \frac{\varepsilon}{L(\mathbf{AX}_{J(S)})}.
%&< \left( \frac{ L_2(\mathbf{A}) }{ 2^{|E|} \max_{j \in [m]} \|\mathbf{A}_j\|_2 } \right) \frac{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) } { L(\mathbf{AX}_{J(S)}) } \min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F}) \\
\end{align}
%\begin{align}
%\delta= \frac{\varepsilon}{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) } = \frac{ C \varepsilon }{ \tilde C } < \frac{L_2(\mathbf{A})}{\tilde C}
%\end{align}
\end{proof}

@@

Let $\mathbf{X}$ and $\mathbf{\bar{X}}$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\bar x}_i$, respectively, and let $I(S) = \{i \in [N]: \text{supp}(\mathbf{x}_i) \subseteq S\}$. From previous arguments, we have for every $S \in E$, the columns of every $n \times k$ submatrix of $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_S\}$.
% the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{I(S)}) > 0$ for all $S \in E$; that is, for every $S \in E$, the columns of every $n \times k$ submatrix of $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_S\}$. 
Suppose there are $(k-1)|E| + 1$ vectors $\mathbf{x}_i$ for which the corresponding $\mathbf{\bar x}_i$ $(i \in J)$ share a support $\bar S$. By the pigeonhole principle, there must be some $S \in E$ supporting $k$ or more of these vectors $\mathbf{x}_i$; let them be indexed by $J \subseteq I(S)$.  By the argument as in the proof of Thm.\ref{DeterministicUniquenessTheorem}, we also have \eqref{rhs222}.

%Fixing $\mathbf{y} \in \text{\rm Span}\{ \mathbf{A}_S \}$, there exists $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_{J}\mathbf{c}$. Setting \mbox{$\mathbf{\bar{y}} = \mathbf{B\bar{X}}_{J}\mathbf{c} \in \text{\rm Span}\{\mathbf{B}_{\bar S}\}$}, we have:
%\begin{align*}
%\|\mathbf{y} - \mathbf{\bar{y}}\|_2 
%&= \|\sum_{i=1}^k c_i(\mathbf{AX}_J - \mathbf{B\bar{X}}_J)_i\|_2
%\leq \varepsilon \sum_{i=1}^k |c_i| \\
%&\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2 
%\leq \frac{\varepsilon}{L_k(\mathbf{AX}_J)} \|\mathbf{y}\|_2,
%\end{align*}
%where the last inequality is by definition of $L_k$. From Def.~\ref{dDef}, it follows that:
%\begin{align}\label{rhs222}
%d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\bar S}\}) 
%\leq \frac{\varepsilon}{ \min_{S \in E}L_k(\mathbf{AX}_{I(S)}) }.
%\end{align}

Our bound on $\varepsilon$ implies that the right-hand side is less than one, so that by \eqref{dimLem} we have $k = \dim(\text{Span}(\mathbf{AX}_J)) \leq \dim(\text{Span}\{\mathbf{B}_{\bar S}\}) \leq |\bar S|$. Hence, if $|E|(k-1) + 1$ or more vectors $\mathbf{\bar x}_i$ share the same support, they cannot be $(k-1)$-sparse, and the number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ must then be bounded from above by $|E|(k-1){ m \choose k-1}$. Taking \eqref{eqn} into account, it follows that at least $N - |E|k(k-1){ m \choose k-1}$ of the vectors $\mathbf{\bar  x}_i$ are $k$-sparse, and there must then be some $N' \subseteq [N]$ for which for each $S \in E$ there are $(k-1){m \choose k}+1$ of the vectors $\mathbf{x}_i$ with $i \in [N']$ supported on $S$ and for which $\mathbf{\bar x}_i$ is $k$-sparse for all $i \in [N']$. The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
\end{proof}

>>>>

\begin{theorem}\label{DeterministicUniquenessTheorem}
%Fix integers $n, \ell$, and $k < m$. 
Let $\mathbf{A}~\in~\mathbb{R}^{n \times m}$ satisfy \eqref{SparkCondition} for $k < m$, and suppose for some $\bar m$ that more than \mbox{$(k-1){\bar m \choose k}$} $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} are supported in general linear position on each set in an $\ell$-regular $E \subseteq {[m] \choose k}$ with the SIP.  There is a constant $C_1 > 0$ for which the following hold for $\varepsilon < L_2(\mathbf{A}) / C_1$.

1) Every matrix $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ with  \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ must have $\bar m \geq m$ and, provided $p = \bar m - \ell(\bar m - m)$ is positive, necessarily satisfy:
\begin{align}\label{Cstable}
\|(\mathbf{A}_J- \mathbf{B}_{\bar J} \mathbf{PD} )_j\|_2 \leq C_1 \varepsilon, \ \  \text{for $j \in J$},
\end{align}
for some $J \in {[m] \choose p}$, $\bar J \in {[\bar m] \choose p}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.

2) Restricting dictionaries and sparse codes to respective $J, \bar{J}$, we furthermore have that if $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and:
\begin{align}\label{b-PDa}
\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\bar x}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,\ \ \   \text{for $i \in [N]$}.
\end{align}
\end{theorem}

@@

%\begin{proposition}
%If $E$ is an $\ell$-regular hypergraph of rank $k$ satisfying the singleton intersection property then $|E| \geq \ell m/k$. 
%\end{proposition}
%Note that every $\ell$-regular hypergraph $E \subseteq {[m] \choose k}$ satisfies: \[|E|k = \sum_{S \in E}|S| = \sum_{i \in [m]} \deg(i) = \ell m.\] 
As mentioned above, it is easy to construct a regular hypergraph $E \subseteq {[m] \choose k}$ with the SIP having cardinality $|E| = m$, implying the lower bound for sample size $N$ from the introduction. In many cases, the SIP can be achieved with $|E| < m$; for example, when $k = \sqrt{m}$ one can take $E$ to be the rows and columns formed by arranging $[m]$ in a square grid.  
%In light of Cor.~\ref{DeterministicUniquenessCorollary}, it would be interesting to determine other such $E$. %[ ** TODO ** can we show for every $k, m$ that there is an $E$ satisfying the SIP with $|E| = \ell m/k$ for every $\ell$ such that $\ell m/k$ is an integer? Then lower bound on $N$ comes from the smallest such $\ell$.]

@@

\begin{corollary}\label{SLCopt}
If the assumptions of Thm.\ref{DeterministicUniquenessTheorem} hold with more than $(k-1)\left[ {\bar m \choose k} + |E|k{\bar m \choose k-1}\right]$ vectors $\mathbf{x}_i$ supported on each $S \in E$, then all matrices $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ solving:
\begin{align}\label{minsum}
\min \sum_{i = 1}^N \|\mathbf{\bar x}_i\|_0 \ \ 
\text{subject to} \ \ \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon, \ \text{for all $i$},
\end{align}
%
necessarily satisfy implications 1) and 2) from Thm.~\ref{DeterministicUniquenessTheorem}.
%must have $\bar m \geq m$ and, provided $p = \bar m - \ell(\bar m - m) > 0$, necessarily satisfy \eqref{Cstable}
%%\begin{align}\label{Cstable}
%%\|(\mathbf{A}_J- \mathbf{B}_{\bar J} \mathbf{PD} )_j\|_2 \leq C_1 \varepsilon, \ \  \text{for  $j \in J$},
%%\end{align}
%for some $J \in {[m] \choose p}$, $\bar J \in {[\bar m] \choose p}$, permutation matrix $\mathbf{P}$, and invertible diagonal matrix $\mathbf{D}$.
\end{corollary}

@@

\begin{corollary}\label{ProbabilisticCor}
Fix $n, m$, and $k$ satisfying \eqref{CScondition} for $\gamma = \gamma_0$, and let the entries of $\mathbf{A} \in \mathbb{R}^{n \times m}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ be drawn independently from probability measures absolutely continuous with respect to the standard Borel measure $\mu$. If more than $(k-1){m \choose k}$ of the vectors $\mathbf{x}_i$ are supported on each $S \in E$ for a regular $E \subseteq {[m] \choose k}$ with the SIP, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
\end{corollary}

@@

\section{Proof of Theorem~\ref{DeterministicUniquenessTheorem} and Corollary~\ref{SLCopt}}\label{DUT}

@@

Given a sequence of vectors $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$, we let $\mathbf{X}$ be the $m \times N$ matrix with columns $\mathbf{x}_i$ and $I(S) := \{i \in [N]: \text{supp}(\mathbf{x}_i) \subseteq S\}$. The constant $C_1$ in Thm.~\ref{DeterministicUniquenessTheorem} is then given by\footnote{Note that $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq \sqrt{k} L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for $S \in E$ and $k$-sparse $\mathbf{c}$. Therefore, $\sqrt{k} L_k(\mathbf{AX}_{I(S)}) \geq k L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$ since $L_k(\mathbf{A}), L_k(\mathbf{X}_{I(S)}) > 0$ by \eqref{SparkCondition} and general linear position of the $\mathbf{x}_i$.  Thus, $C_1 > 0$.  }:
\begin{align}\label{Cdef1}
C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E) := \frac{ C_2(\mathbf{A}, E) } { \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }.
\end{align}

The constant $C_2 = C_2(\mathbf{A}, E)$ is defined below in terms of one used in \cite{Deutsch12} to analyze the convergence of the alternating projections algorithm.
% for projecting a point onto the intersection of a set of subspaces. 
We use it to bound the distance between a point and the intersection of a set of subspaces given an upper bound on its distance from each subspace individually.

@@

\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
%We begin by showing that for every $S \in E$ there is some $S' \in {[m] \choose k}$ for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_S'\})$ is controlled by $\varepsilon$. Fix $S \in E$. Since there are $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $S' \in {[m] \choose k}$ and some set of $k$ indices $J(S)$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\bar x}_i$ with $i \in J(S)$ are contained in $S$ and $S'$, respectively.
%%% No |S| = k assumption %%%
We shall show that for every $S \in E$ there is some $\bar S \in {[m] \choose k}$, for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\bar S}\})$ is controlled by $\varepsilon$. Applying Lem.~\ref{MainLemma} with the map $\pi$ defined by $S \mapsto \bar S$ then completes the proof.  Since there are $(k-1){\bar m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $\bar S \in {[\bar m] \choose k}$ and some set of $k$ indices $K$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\bar x}_i$ with $i \in K$ are contained in $S$ and $\bar S$, respectively.

%Let $\mathbf{X}$ and $\mathbf{\bar{X}}$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\bar x}_i$, respectively. 
It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{I(S)}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_K$ form a basis for $\text{\rm Span}\{\mathbf{A}_{S}\}$. Fixing $\mathbf{y} \in \text{\rm Span}\{\mathbf{A}_{S}\}$, there exists $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$. Setting \mbox{$\mathbf{\bar{y}} = \mathbf{B\bar{X}}_K\mathbf{c} \in \text{\rm Span}\{\mathbf{B}_{\bar S}\}$}, we have:
\begin{align*}
\|\mathbf{y} - \mathbf{\bar{y}}\|_2 
&= \|\sum_{i=1}^k c_i(\mathbf{AX}_K - \mathbf{B\bar{X}}_K)_i\|_2
\leq \varepsilon \sum_{i=1}^k |c_i| \\
&\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2 
%\leq \frac{\varepsilon \sqrt{k}}{L(\mathbf{A}X_{J(S)})} \|\mathbf{A}X_{J(S)}\mathbf{c}\|_2 
\leq \frac{\varepsilon}{L_k(\mathbf{AX}_K)} \|\mathbf{y}\|_2,
\end{align*}
where the last inequality is by definition of $L_k$. Finally, from Def.~\ref{dDef}, it follows that for all $S \in E$,
\begin{align}\label{rhs222}
d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\bar S}\}) 
\leq \frac{\varepsilon}{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }.
\end{align}
\end{proof}

@@

We will show that no more than $(k-1)|E|$ vectors $\mathbf{\bar x}_i$ can share a support of cardinality less than $k$. 
%Let $\mathbf{X}$ and $\mathbf{\bar{X}}$ be the $m \times N$ and $\bar m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\bar x}_i$, respectively, and let $I(S) = \{i \in [N]: \text{supp}(\mathbf{x}_i) \subseteq S\}$. 
From previous arguments, we have for every $S \in E$, the columns of every $n \times k$ submatrix of $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_S\}$.
% the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{I(S)}) > 0$ for all $S \in E$; that is, for every $S \in E$, the columns of every $n \times k$ submatrix of $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_S\}$. 
Suppose there are more than $(k-1)|E|$ vectors $\mathbf{\bar x}_i$ sharing a support $\bar S$ of cardinality less than $k$. By the pigeonhole principle, there must be some $S \in E$ supporting $k$ or more of the corresponding $\mathbf{x}_i$; let them be indexed by $K \subseteq I(S)$.  By the argument as in the proof of Thm.\ref{DeterministicUniquenessTheorem}, we also have \eqref{rhs222}. Since our bound on $\varepsilon$ implies that the right-hand side of \eqref{rhs222} is less than one, by \eqref{dimLem} we have $k = \dim(\text{Span}(\mathbf{A}_S)) \leq \dim(\text{Span}\{\mathbf{B}_{\bar S}\}) \leq |\bar S|$, a contradiction.

Hence, the number of $(k-1)$-sparse vectors $\mathbf{\bar x}_i$ is no greater than $|E|(k-1){ m \choose k-1}$. Taking \eqref{eqn} into account, it follows that at least $N - |E|k(k-1){ m \choose k-1}$ of the vectors $\mathbf{\bar  x}_i$ are $k$-sparse. Therefore, more than $(k-1){m \choose k}$ of the vectors $\mathbf{x}_i$ supported on each $S \in E$ have corresponding $\mathbf{\hat x}_i$ that are also $k$-sparse. The result now follows directly from Thm.~\ref{DeterministicUniquenessCorollary}.
\end{proof}
